---
title: "Reproducible Research: Peer Assessment 1"
author: "Laercio J Oliveira"
date: "January 10, 2016"
output: 
  html_document:
    keep_md: true
---


## Loading and preprocessing the data

Reading the data into data frame
```{r}
data <- read.csv("activity.csv", na.strings = "NA")
str(data)
```


```{r}
summary(data)
```


## What is mean total number of steps taken per day?

#### 1. Calculate the total number of steps taken per day
```{r, echo=TRUE}
sumStepsPerDay <- aggregate(steps ~ date, data, sum)
```

####  2. Make a histogram of the total number of steps taken each day
```{r, echo=TRUE}
hist(sumStepsPerDay$steps,col="orange",breaks=30,main="Total steps per day",xlab="Steps per  day")
```

#### 3. Calculate and report the mean and median of the total number of steps taken per day
```{r, echo=TRUE}
summary(sumStepsPerDay)
```
Mean = 10766 and Median = 10765



## What is the average daily activity pattern?

#### 1. Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)  

```{r, echo=TRUE}
library(dplyr,quietly = TRUE)
grouped <- group_by(data, interval)
d_a_pattern <- summarise(grouped, mean=mean(steps, na.rm=TRUE))
plot(d_a_pattern$interval , d_a_pattern$mean,type = "l", col = "red", xaxt = "n",xlab="Intervals", ylab = "Average across all days")
```

#### 2. Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?

```{r, echo=TRUE}
filter(d_a_pattern, mean==max(mean))
```
